Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-01-15 lloveras_2020_Albert_Section1.tex

\begin{abstract}
Observational techniques play an essential role in advancing our understanding of the physics of the solar corona. They provide validation data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, key to improve their space weather forecasting capabilities. Solar rotational tomography is currently the sole observational technique that provides an empirical 3D description of some {of the fundamental} plasma parameters of the solar corona at a global scale. Based on \diego{extreme ultraviolet} data of space borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun. We carry out a study of the corona combining {DEMT} reconstructions with MHD simulations using the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework. Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the declining} phase of SC 24. The 3D tomographic and MHD models are analysed and compared in distinct coronal magnetic structures. {We report in quantitative detail on the 3D termodinamic structure of the inner corona as revealed by the DEMT analysis. We show in particular the existence of diverse types of temperature structures in the low and mid latitudes of the streamer belt, and that the heating energy required to keep them stable may be accounted for by Alfvén waves. We show that the latest version of the AWSoM model results agree with DEMT reconstructions to within a $\approx 20\%$ accuracy or better. We report on aspects of the AWSoM model that could be improved to better reproduce the DEMT results, in particular concerning the source region of the fast/slow solar winds.}
\end{abstract}

@@

To study the global coronal 3D structure, solar rotational tomography (SRT) proved to be a powerful tool. Based on solar rotation, allow instruments to compile a time series of images that cover the entire corona.

{Based on time-series of \diego{extreme ultraviolet (EUV)} images, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the \diego{quiet-Sun low corona at a global scale.} The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}. Using solar rotation time series of EUV images taken in channels sensitive to different temperatures, the technique allows calculation of 3D maps of electron density and temperature in the heliocentric height range $1.0\,\mrsun$ to $1.2\,\mrsun$ as summarized in Section \ref{demt}.

\diego{
A combination of the DEMT and global magnetic models has provided useful insight into the 3D thermodynamical structure of the global quiet-Sun corona. For the first time we combined DEMT with coronal magnetic field modeled by a magnetohydrodynamic (MHD) model. Using the latest version of the Alfvén Wave Solar Model (AWSoM) of the Space Weather Modeling Framework, which provides a global magnetohydrodynamic (MHD) model coronal magnetic field and coronal thermodynamics,a combination of DEMT and AWSoM results 
}
We carry out a quantitatively detailed comparative DEMT analysis of the Carrington Rotation (CR)-2082 during the Solar Cycle (SC) 23/24 minimum and CR-2208 during the declining fase of SC 24. To study CR-2082 data taken by the \textit{Extreme UltraViolet Imager Behind} (EUVI-B) on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) was used, while data taken by the \textit{Atmospheric Imaging Assembly instrument} (AIA), on board the \textit{Solar Dynamics Observatory} (SDO) mission was used to study CR-2208.

\diego{
Complementary to this, the coronal magnetic field of the global corona can be modeled
by means of potential field source surface (PFSS) or even magnetohydrodynamics (MHD)
models. A combination of the DEMT and global magnetic models has provided useful in-
sight into the 3D thermodynamical structure of the global quiet-Sun corona
}

\diego{El parrafo de abajo lo pondria en la seccion 2.1}
In DEMT, the low corona in the height range $1.0-1.25\,\mrsun$ is discretized in a spherical computational grid. The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions. The cadence of the data time-series is set to 6\,hr. The main product of the technique is the local DEM (LDEM) at each volxel, a measure of the temperature distribution of the plasma contained in it. A recent review by \citet{vasquez_2016} summarizes the DEMT works up until then. More recently \citet{lloveras_2017} applied DEMT to study the last two solar minima, and \citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona.}

@@

Once the LDEM is determined at each voxel, {the LDEM-averaged squared electron density $\Nm^2$ and electron temperature $\Tm$} in the voxel can be computed by taking its zeroth and first moments over temperature. More specifically, at the $i$-th voxel,
{
\begin{eqnarray}\label{momento1}
 \Nsqmi = \langle \Ne^2 \rangle_i &=& \int\,\textrm{d}T\,\LDEM_i(T),\label{Ne} \\ 
\label{momento2}
 \Tmi  = \langle \Te \rangle_i &=& \frac{1}{\langle \Ne^2 \rangle_i}\,\int\,\textrm{d}T\,T\,\LDEM_i(T),\label{Tm} 
\end{eqnarray}
}

@@

{The energy balance given by Equation (\ref{Balance}) is then integrated in the volume of any given coronal magnetic flux tube. Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal conditon of the magnetic field, a field-line integrated version of that energy balance is found,
\begin{equation}\label{FluxBalance}
\phi_h = \phi_r + \phi_c.
\end{equation}
\noindent
where the line integrated flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},} \\

@@

{Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer regions of the equatorial streamer belt, exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature. In both rotations also, type III legs in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I legs in the core of the equatorial streamer.}

@@

{Concerning the DEMT reconstructions, throughout the magnetically closed region of both rotations, we find that type 0, I and II legs are associated to increasingly outer regions of the equatorial streamer belt, and exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature. For both target rotations we find that down legs populate the low latitudes of the streamer belt, while up legs dominate its mid-latitudes. Also, in the case of CR-2082 the fraction of down legs is significantly larger than for CR-2208. These findings are consistent with previous studies by \citet{huang_2012} and \citet{nuevo_2013}. In the case of the latter, they include in their analysis target CR-2081, which is a rotation almost identical to our target CR-2082. Our results for target CR-2082 compare very well with those of \citet{nuevo_2015} and \citet{lloveras_2017} for target CR-2081. As our study uses the improved version of the DEMT technique, such comparison provided a consistency check for the changes implemented in the DEMT technique.}

@@

{A detailed empirical description of the 3D termodynamic structure of the inner corona at a global scale is curently only possible with tomographic techniques, such as DEMT. Using tomographic results for continuous validation of 3D MHD models is of high relevance for the continued improvement of models. In a follow up article we will analyse whit DEMT and 3D MHD modeling new target rotations of the current solar minimum between SCs 24 and 25, in particular the rotations conrresponding to the 2019 and 2020 total solar eclipses.}

\begin{acks}
D.G.Ll. and C.M.C. {acknowledge} CONICET doctoral {fellowships} (Res. Nr. 4870) to IAFE that supported {their} participation in this research. {D.G.Ll, A.M.V., F.A.N. and C.M.C. acknowledge ANPCyT grant 2016/0221 to IAFE that partially supported their participation in this research. A.M.V. also acknowledges UBACyT grant \diego{XXXX} to FCEyN-UBA and IAFE that partially supported his participation in this research.}
\end{acks}
\\
\\
\begin{footnotesize}
 Disclosure of Potential Conflicts of Interest: The authors declare that they have no conflicts of interest.
\end{footnotesize}
\bibliographystyle{spr-mp-sola}
\bibliography{solphys_dglloveras}

>>>>

\begin{abstract}
Observational techniques play an essential role in advancing our understanding of the physics of the solar corona. They provide validation data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, key to improve their space weather forecasting capabilities. Solar rotational tomography (SRT) is currently the sole observational technique that provides an empirical 3D description of some {of the fundamental} plasma parameters of the solar corona at a global scale. Based on EUV data of space borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun. We carry out a study of the corona combining {DEMT} reconstructions with MHD simulations using the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF). Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the declining} phase of SC 24. The 3D tomographic and MHD models are analysed and compared in distinct coronal magnetic structures. {We report in quantitative detail on the 3D termodinamic structure of the inner corona as revealed by the DEMT analysis. We show in particular the existence of diverse types of temperature structures in the low and mid latitudes of the streamer belt, and that the heating energy required to keep them stable may be accounted for by Alfvén waves. We show that the latest version of the AWSoM model results agree with DEMT reconstructions to within a $\approx 20\%$ accuracy or better. We report on aspects of the AWSoM model that could be improved to better reproduce the DEMT results, in particular concerning the source region of the fast/slow solar winds.}
\end{abstract}

@@

{Based on time-series of EUV images, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the solar corona. The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}. In DEMT, the low corona in the height range $1.0-1.25\,\mrsun$ is discretized in a spherical computational grid. The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions. The cadence of the data time-series is set to 6\,hr. The main product of the technique is the local DEM (LDEM) at each volxel, a measure of the temperature distribution of the plasma contained in it. A recent review by \citet{vasquez_2016} summarizes the DEMT works up until then. More recently \citet{lloveras_2017} applied DEMT to study the last two solar minima, and \citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona.}

@@

Once the LDEM is determined at each voxel, {the LDEM-averaged squared electron density $\Nm^2$ and electron temperature $\Tm$} in the voxel can be computed by taking its zeroth and first moments over temperature. More specifically, at the $i$-th voxel,
{
\begin{eqnarray}\label{momento1}
 \Nsqmi = \langle \Ne^2 \rangle_i &=& \int\,\textrm{d}T\,\LDEM_i(T),\label{Ne} \\ 
\label{momento2}
 \Tmi  = \langle \Te \rangle_i &=& \frac{1}{\langle \Ne^2 \rangle_i}\,\int\,\textrm{d}T\,T\,\albert{\LDEM_i(T).}\label{Tm} 
\end{eqnarray}
}

@@

The energy balance given by Equation (\ref{Balance}) is then integrated in the volume of any given coronal magnetic flux tube. Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal conditon of the magnetic field, a field-line integrated version of that energy balance is found,

\begin{equation}\label{FluxBalance}
\phi_h = \phi_r + \albert{\phi_c,}
\end{equation}

\noindent
where the line integrated flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},

@@

{Throughout the magnetically closed region of both rotations, type 0, I and II legs, associated to  increasingly outer \albert{layers} of the equatorial streamer belt, exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature. In both rotations also, type III legs in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I legs in the core of the equatorial streamer.}

@@

{Concerning the DEMT reconstructions, throughout the magnetically closed region of both rotations, we find that type 0, I and II legs are associated to increasingly outer \albert{layers} of the equatorial streamer belt, and exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature. For both target rotations we find that down legs populate the low latitudes of the streamer belt, while up legs dominate its mid-latitudes. Also, in the case of CR-2082 the fraction of down legs is significantly larger than for CR-2208. These findings are consistent with previous studies by \citet{huang_2012} and \citet{nuevo_2013}. In the case of the latter, they include in their analysis target CR-2081, which is a rotation almost identical to our target CR-2082. Our results for target CR-2082 compare very well with those of \citet{nuevo_2015} and \citet{lloveras_2017} for target CR-2081. As our study uses the improved version of the DEMT technique, such comparison provided a consistency check for the changes implemented in the DEMT technique.}

@@

A detailed empirical description of the 3D termodynamic structure of the inner corona at a global scale is curently only possible with tomographic techniques, such as DEMT. Using tomographic results for continuous validation of 3D MHD models is of high relevance for the continued improvement of models. In \albert{follow up articles} we will \albert{carry out the 3D DEMT reconstruction and MHD modeling of} new target rotations \albert{selected from} the current solar minimum \albert{epoch} between SCs 24 and 25, \albert{as well as rotation CR-2219 corresponding to the July 2nd 2019 total solar eclipse.}

\begin{acks}
D.G.Ll. and C.M.C. {acknowledge} CONICET doctoral {fellowships} (Res. Nr. 4870) to IAFE that supported {their} participation in this research. {D.G.Ll, A.M.V., F.A.N. and C.M.C. acknowledge ANPCyT grant 2016/0221 to IAFE that partially supported their participation in this research. A.M.V. also acknowledges UBACyT grant \albert{XXXX} to FCEyN-UBA and IAFE that partially supported his participation in this research.}
\end{acks}

\bibliographystyle{spr-mp-sola}
\bibliography{solphys_dglloveras}
